Inefficient Concessions and Mediation

### 2020-12-02 notes.tex
Develop notes on e<1 mediation case

\DeclareMathOperator*{\argmax}{arg\,max}
\usepackage{xcolor}
\hbadness=10000

@@

Equation \ref{eqn:IClow} is the general form of the IC constraint. In the next step in Section~\ref{sec:e1}, I let the gifts cancel out because we assume in that section that $e=1$. I need to go back to Equation \ref{eqn:IClow} here since $e$ is not assumed to be 1.
\[
	X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-pg_h+peg_h
\]
Leaving the two gift terms on the end intact, I simplify in the same way as in Section $\ref{sec:e1}$ to arrive at the correct analog to Equation~\ref{eq:lowICex}.
		\begin{multline*}
			W\left(m_1 + \left(1-\al_1\right)eg_2\right)-D\left(m_2 + \left(1-\al_2\right)eg_1\right) \geq \\
			\left(1-\de^l\right) \left[T\left(s_2 + \al_2eg_1\right) + W\left(m_1 + \left(1-\al_1\right)eg_2\right) \right] \\
			+ \de^l \left(W\left(m_1 + \left(1-\al_1\right)eg_2\right)-D\left(m_2 + \left(1-\al_2\right)eg_1\right)\right) -pg_h+peg_h
		\end{multline*}
	\begin{itemize}
		\item We assume $s_1,s_2,m_1,m_2$ to all be 1 to be consistent with Section 4.2
			\begin{multline*}
				W\left(1 + \left(1-\al_1\right)eg_2\right)-D\left(1 + \left(1-\al_2\right)eg_1\right) \geq \\
			\left(1-\de^l\right) \left[T\left(1 + \al_2eg_1\right) + W\left(1 + \left(1-\al_1\right)eg_2\right) \right] \\
			+ \de^l \left(W\left(1 + \left(1-\al_1\right)eg_2\right)-D\left(1 + \left(1-\al_2\right)eg_1\right)\right) -pg_h+peg_h
			\end{multline*}
		\item We know that there are no gifts exchanged for $X^l_{FF}$, so $g_1 = g_2 = 0$ on the LHS. On the RHS, gifts ARE exchanged because player 2 is a high type and the low type of player 1 lied. So we can set $g_1 = g_2 = g_M$:
			\begin{multline*}
				W\left(1 \right)-D\left(1 \right) \geq
			\left(1-\de^l\right) \left[T\left(1 + \al_2eg_M\right) + W\left(1 + \left(1-\al_1\right)eg_M\right) \right] \\
			+ \de^l \left(W\left(1 + \left(1-\al_1\right)eg_M\right)-D\left(1 + \left(1-\al_2\right)eg_M\right)\right) -pg_M+peg_M
			\end{multline*}
		\item With $a_1 = 0$ and $a_2 = 1$ (Recall the discussion above Equation~\ref{eqn:alphas}), we have
			\[
				W - D \geq \left(1-\de^l\right) \left[T\left(1 + eg_M\right) + W\left(1 + eg_M\right) \right] 
			+ \de^l \left(W\left(1 + eg_M\right) - D\right) -pg_M+peg_M
			\]
		\item It's time to start rearranging:
			\[
				pg_M\left(1 - e\right) \geq \left(1-\de^l\right) \left[T\left(1 + eg_M\right) + W\left(1 + eg_M\right) \right] 
			+ \de^l W\left(1 + eg_M\right) - \de^l D - W + D
			\]
			\[
				pg_M\left(1 - e\right) \geq \left(1-\de^l\right) \left[T\left(1 + eg_M\right) + W\left(1 + eg_M\right) \right] 
			+ \de^l W\left(1 + eg_M\right) + \left(1 - \de^l\right) D - W
			\]
			\begin{multline*}
			  	pg_M\left(1 - e\right) \geq T\left(1 + eg_M\right) + W\left(1 + eg_M\right) -\de^l T\left(1 + eg_M\right) -\de^l W\left(1 + eg_M\right) \\
			+ \de^l W\left(1 + eg_M\right) + \left(1 - \de^l\right) D - W
			\end{multline*}
			\[
				pg_M\left(1 - e\right) \geq T\left(1 + eg_M\right) + W\left(1 + eg_M\right) -\de^l T\left(1 + eg_M\right) + \left(1 - \de^l\right) D - W
			\]
			\[
				pg_M\left(1 - e\right) \geq T\left(1 + eg_M\right) + Weg_M -\de^l T\left(1 + eg_M\right) + \left(1 - \de^l\right) D
			\]
			\[
				pg_M\left(1 - e\right) \geq \left(1 - \de^l\right) T\left(1 + eg_M\right) + Weg_M + \left(1 - \de^l\right) D
			\]
	\end{itemize}

\textbf{NOW, it's time to explore this equation and see if it's even possible to pick a gift high enough and an $e$ low enough to satisfy the low type's incentive constraint}
\begin{itemize}
	\item Digitize handwritten notes pages 1-3
\end{itemize}

@@

\end{itemize}
IC constraint:
\[
  X_{FF}^l \geq p X_{FT}^l + (1-p) X_{FF}^l - g
\]
Expanded in basic terms (without efficiency issues)
\[
  \frac{W-D}{1-\de} \geq p \left[T + W + \frac{\de}{1-\de}\left(W-D\right)\right] + (1-p) \frac{W-D}{1-\de} - g
\]
Multiply through by $\left(1-\de \right)$
\[
  W-D \geq p\left(1-\de \right) \left[T + W\right] + p\de \left(W-D\right) + (1-p) \left[W-D\right] - \left(1-\de \right) g
\]
Now add complexity from Table 2
\begin{multline*}
  W(1+(1-\al_1)g_2)-D(1+(1-\al_2)g_1) \geq \\
	p\left(1-\de \right) \left[T(1+\al_2 g_1) + W(1+(1-\al_1)g_2)\right] + p\de \left(W(1+(1-\al_1)g_2)-D(1+(1-\al_2)g_1)\right) \\ + (1-p) \left[W(1+(1-\al_1)g_2)-D(1+(1-\al_2)g_1)\right] - \left(1-\de \right) g
\end{multline*}
Substitute in $\al_1 = 0$ everywhere since this is the IC for a low-type of player 1:
\begin{multline*}
  W(1+g_2) - D(1+(1-\al_2)g_1) \geq \\
	p\left(1-\de \right) \left[T(1+\al_2 g_1) + W(1+g_2) \right] + p\de \left(W(1+g_2) - D(1+(1-\al_2)g_1)\right) \\ + (1-p) \left[W(1+g_2) - D(1+(1-\al_2)g_1)\right] - \left(1-\de \right) g
\end{multline*}
Set $g_1 = 0$ on the LHS and $g_1 = g$ on the RHS:
\begin{multline*}
  W(1+g_2) - D \geq \\
	p\left(1-\de \right) \left[T(1+\al_2 g) + W(1+g_2) \right] + p\de \left(W(1+g_2) - D(1+(1-\al_2)g)\right) \\ + (1-p) \left[W(1+g_2) - D(1+(1-\al_2)g)\right] - \left(1-\de \right) g
\end{multline*}
Set $g_2 = 0$ and $\al_2 = 0$ wherever there is a $(1-p)$ and $g_2 = g$ and $\al_2 = 1$ wherever there is a $p$:
\begin{multline*}
  pW(1+g) + (1-p)W - D \geq \\
	p\left(1-\de \right) \left[T(1+g) + W(1+g) \right] + p\de \left(W(1+g) - D\right) \\ + (1-p) \left[W - D(1+g)\right] - \left(1-\de \right) g
\end{multline*}
Expand
\begin{multline*}
  pW + pWg + W - pW - D \geq \\
	\left(p-p\de \right) \left[T+Tg + W+Wg \right] + p\de \left(W+Wg - D\right) \\ + (1-p) \left[W - D -Dg\right] - \left(1-\de \right) g
\end{multline*}
Cancel some like terms and move $\left(1-\de \right) g$ to LHS
\begin{multline*}
  \left(1-\de \right) g + pWg + W - D \geq \\
	p\left[T+Tg + W+Wg \right] -p\de \left[T+Tg \right] - p\de D \\ + (1-p) \left[W - D -Dg\right] 
\end{multline*}
Do some more canceling and expanding
\begin{multline*}
  \left(1-\de \right) g + W - D \geq \\
	p\left[T+Tg + W\right] -p\de T -p\de Tg - p\de D \\ + W - D -Dg -pW +pD +pDg
\end{multline*}
\[
  \left(1-\de \right) g \geq 
	pT+pTg + pW -p\de T -p\de Tg - p\de D  -Dg -pW +pD +pDg
\]
\[
  \left(1-\de \right) g \geq pT+pTg -p\de T -p\de Tg - p\de D  -Dg +pD +pDg
\]
Now just rearrange to get all the $g$ terms on the left
\[
  \left(1-\de \right) g -pTg + p\de Tg + Dg - pDg\geq pT -p\de T - p\de D +pD
\]
\[
  \left[\left(1-\de \right) -p(1-\de)T +(1-p)D\right]g \geq p(1-\de)(T + D)
\]
\[
  g \geq \frac{p(1-\de)(T + D)}{\left(1-\de \right) -p(1-\de)T +(1-p)D}
\]
In comparing to the minimum separating gift when $e=0$, which is
\[
  g^* \geq \frac{p(1-\de)(T + D)}{\left(1-\de \right)}
\]
We can simplify to see that the minimum gift when $e=1$ is larger when
\[
  (1-\de)pT > (1-p)D
\]

>>>>

\DeclareMathOperator*{\argmax}{arg\,max}
\usepackage[dvipsnames]{xcolor}
\hbadness=10000

@@

Equation \ref{eqn:IClow} is the general form of the IC constraint. In the next step in Section~\ref{sec:e1}, I let the gifts cancel out because we assume in that section that $e=1$. I need to go back to Equation \ref{eqn:IClow} here since $e$ is not assumed to be 1.
\[
	X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-pg_h+peg_h
\]
Leaving the two gift terms on the end intact, I simplify in the same way as in Section $\ref{sec:e1}$ to arrive at the correct analog to Equation~\ref{eq:lowICex}.
		\begin{multline*}
			W\left(m_1 + \left(1-\al_1\right)eg_2\right)-D\left(m_2 + \left(1-\al_2\right)eg_1\right) \geq \\
			\left(1-\de^l\right) \left[T\left(s_2 + \al_2eg_1\right) + W\left(m_1 + \left(1-\al_1\right)eg_2\right) \right] \\
			+ \de^l \left(W\left(m_1 + \left(1-\al_1\right)eg_2\right)-D\left(m_2 + \left(1-\al_2\right)eg_1\right)\right) -pg_h+peg_h
		\end{multline*}
	\begin{itemize}
		\item We assume $s_1,s_2,m_1,m_2$ to all be 1 to be consistent with Section 4.2
			\begin{multline*}
				W\left(1 + \left(1-\al_1\right)eg_2\right)-D\left(1 + \left(1-\al_2\right)eg_1\right) \geq \\
			\left(1-\de^l\right) \left[T\left(1 + \al_2eg_1\right) + W\left(1 + \left(1-\al_1\right)eg_2\right) \right] \\
			+ \de^l \left(W\left(1 + \left(1-\al_1\right)eg_2\right)-D\left(1 + \left(1-\al_2\right)eg_1\right)\right) -pg_h+peg_h
			\end{multline*}
		\item We know that there are no gifts exchanged for $X^l_{FF}$, so $g_1 = g_2 = 0$ on the LHS. On the RHS, gifts ARE exchanged because player 2 is a high type and the low type of player 1 lied. So we can set $g_1 = g_2 = g_M$:
			\begin{multline*}
				W\left(1 \right)-D\left(1 \right) \geq
			\left(1-\de^l\right) \left[T\left(1 + \al_2eg_M\right) + W\left(1 + \left(1-\al_1\right)eg_M\right) \right] \\
			+ \de^l \left(W\left(1 + \left(1-\al_1\right)eg_M\right)-D\left(1 + \left(1-\al_2\right)eg_M\right)\right) -pg_M+peg_M
			\end{multline*}
		\item With $a_1 = 0$ and $a_2 = 1$ (Recall the discussion above Equation~\ref{eqn:alphas}), we have
			\[
				W - D \geq \left(1-\de^l\right) \left[T\left(1 + eg_M\right) + W\left(1 + eg_M\right) \right] 
			+ \de^l \left(W\left(1 + eg_M\right) - D\right) -pg_M+peg_M
			\]
		\item It's time to start rearranging:
			\[
				pg_M\left(1 - e\right) \geq \left(1-\de^l\right) \left[T\left(1 + eg_M\right) + W\left(1 + eg_M\right) \right] 
			+ \de^l W\left(1 + eg_M\right) - \de^l D - W + D
			\]
			\[
				pg_M\left(1 - e\right) \geq \left(1-\de^l\right) \left[T\left(1 + eg_M\right) + W\left(1 + eg_M\right) \right] 
			+ \de^l W\left(1 + eg_M\right) + \left(1 - \de^l\right) D - W
			\]
			\begin{multline*}
			  	pg_M\left(1 - e\right) \geq T\left(1 + eg_M\right) + W\left(1 + eg_M\right) -\de^l T\left(1 + eg_M\right) -\de^l W\left(1 + eg_M\right) \\
			+ \de^l W\left(1 + eg_M\right) + \left(1 - \de^l\right) D - W
			\end{multline*}
			\[
				pg_M\left(1 - e\right) \geq T\left(1 + eg_M\right) + W\left(1 + eg_M\right) -\de^l T\left(1 + eg_M\right) + \left(1 - \de^l\right) D - W
			\]
			\[
				pg_M\left(1 - e\right) \geq T\left(1 + eg_M\right) + Weg_M -\de^l T\left(1 + eg_M\right) + \left(1 - \de^l\right) D
			\]
			\begin{equation}
				pg_M\left(1 - e\right) \geq \left(1 - \de^l\right) T\left(1 + eg_M\right) + Weg_M + \left(1 - \de^l\right) D
				\label{eq:examine}
			\end{equation}
	\end{itemize}

\textbf{NOW, it's time to explore this equation and see if it's even possible to pick a gift high enough and an $e$ low enough to satisfy the low type's incentive constraint}. Continuing on from Equation~\ref{eq:examine} and simplifying so that $g_M = g$ and $\de^l = \de$,
\[
	pg\left(1 - e\right) \geq \left(T - \de T \right) \left(1 + eg\right) + Weg + \left(1 - \de \right) D
\]
	\begin{itemize}
		\item Distributing AGAIN
			\[
				pg	\left(1 - e\right) \geq T + Teg - \de T - \de T eg + Weg + \left(1 - \de \right) D
			\]
			\[
				pg	\left(1 - e\right) \geq \left(1 - \de \right) T + \left(1 - \de \right) D + Teg - \de T eg + Weg
			\]
			\begin{equation}
				pg - pge \geq \left(1 - \de \right) \left( T + D \right) + eg \left( T - \de T + W \right)
				\label{eq:split}
			\end{equation}
		\item From here we can solve either for the constraint in terms of $g$ or in terms of $e$
			\begin{itemize}
				\item First solve for $g$ starting from Expression~\ref{eq:split}:
					$$pg - pge \geq \left(1 - \de \right) \left( T + D \right) + eg \left( T - \de T + W \right)$$
					$$pg - pge - eg \left( T - \de T + W \right)\geq \left(1 - \de \right) \left( T + D \right)$$
					\begin{equation}
						g \left(p - e \left( p + T - \de T + W \right) \right) \geq \left(1 - \de \right) \left( T + D \right)
						\label{eq:g1}
					\end{equation}
					\begin{equation}
						g \geq \frac{\left(1 - \de \right) \left( T + D \right)}{p - e \left( p + T - \de T + W \right)}
						\label{eq:g2}
					\end{equation}
						\begin{itemize}
							\item THIS ASSUMES {\color{red} $p - e \left( p + T - \de T + W \right)$ IS POSITIVE}
								\begin{itemize}
									\item Note that if we set $e=0$, this is a very simple constraint on $g$
										\begin{equation}
											g \geq \frac{\left(1 - \de \right) \left( T + D \right)}{p}
											\label{eq:g3}
										\end{equation}
								\end{itemize}
							\item $T+D$, $1 - \de $ non-negative by assumption $\Rightarrow$ RHS of Expression~\ref{eq:g1} non-negative
								\begin{itemize}
									\item If $\left(p - pe - e \left( T - \de T + W \right) \right)$ is negative, the only way the IC constraint in Expression~\ref{eq:g1} can hold is if $g<0$. AGAIN WITH THE NEGATIVE GIFTS.
								\end{itemize}
							\item To compare to the optimal gift size in the other sections:
								\begin{itemize}
									\item In Section 3 (Concessions Separating Equilibrium): $p\left(T+D\right)$
									\item Material value with $e=0$ same as in Section 3: $p\left(T+D\right)$
									\item Material value with $e=1$:
										\begin{equation}
											g \geq \frac{p(1-\de)(T + D)}{\left(1-\de \right) -p(1-\de)T +(1-p)D}
											\label{eq:g4}
										\end{equation}
									\item Under the assumption that payoffs are multiplied by something linear like $1 + \al_2 g_1$, there's no reason to choose any intermediate value of $e$. The mediator, of course, can specify an intermediate value.
									\item We can simplify to see that the minimum gift when $e=1$ is larger when
										\[
											(1-\de)pT > (1-p)D
										\]
								\end{itemize}
						\end{itemize}

				\item Now solve for $e$ starting from Expression~\ref{eq:split}:
					$$pg - \left(1 - \de \right) \left( T + D \right) \geq pge + eg \left( T - \de T + W \right)$$
					\begin{equation}
						pg - \left(1 - \de \right) \left( T + D \right) \geq eg \left( p + T - \de T + W \right)
						\label{eq:g5}
					\end{equation}
						\begin{itemize}
							\item {\color{red} $g \left( p + T - \de T + W \right)$ is non-negative as long as $g$ is positive}: $p, 1-\de, T$ and $W$ are all assumed non-negative and $T+D > W$ so that $T$ is strictly positive. It can only possibly be zero if $p=0$ and $\de = 1$.
								\begin{itemize}
									\item For the IC constraint to hold then (with non-negative gifts), we must at least have {\color{red} $pg - \left(1 - \de \right) \left( T + D \right)$ non-negative, which requires $g$ to be set according to Expression~\ref{eq:g3}}. This only works if $e$ is set to zero; otherwise we need to look back at Expression~\ref{eq:g2}. This is just a weak condition that, if violated, means the IC constraint does not hold.
								\end{itemize}
							\item If {\color{red} $g \left( p + T - \de T + W \right)$ is positive}, we can divide through to get
								$$\frac{pg - \left(1 - \de \right) \left( T + D \right)}{g \left( p + T - \de T + W \right)} \geq e$$
						\end{itemize}
					\item To get a sense of the magnitudes, I will plug $g = p \left(T+D\right)$ from the $e=0$ CSE case (just because it's easier to work with than the optimal gift when $e=1$ into Expression~\ref{eq:g5}. First I divide through by $g$ {\color{blue}(this is okay if $g$ is assumed to be positive)}
						\begin{equation}
							p - \frac{\left(1 - \de \right) \left( T + D \right)}{g} \geq e \left( p + T - \de T + W \right)
							\label{eq:g6}
						\end{equation}
						$$p - \frac{\left(1 - \de \right) \left( T + D \right)}{p \left(T+D\right)} \geq e \left( p + T - \de T + W \right)$$
						$$p - \frac{1 - \de}{p } \geq e \left( p + T - \de T + W \right)$$
							\begin{itemize}
								\item For the LHS to be positive, we need $p^2 \geq 1 - \de$, e.g. if $p = 0.5$, we need $\de \geq .75$
								\item Parameterization that is in the paper now:
									\begin{itemize}
										\item Let $T = 10$, $W=8$ and $D = 5$
										\item Threshold for high types to separate when concessions do not have future material value is $\de = \frac{8}{10+5} = .5\overline{3}$. Let $\de_h = .6$ and $\de_l = .3$. Assume $p = .2$. By Theorem 2, separation through concessions is possible.
										\item Minimum separating concession is $g^1 = \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D} = .\overline{63}$
										\item Minimum patience level required for separation is $\de_h^1 = D(1-p)+1-pT + \frac{p(W-(T+D))}{g^1} = .7\overline{9}.$ Because the specified $\de_h$ is not involved in any of these calculations, we can see that for any $\de_h \in [.5\overline{3},.7\overline{9})$, separating through concessions is possible when concessions have no material value but is not possible when they do have future material value.
									\end{itemize}
							\end{itemize}

			\end{itemize}
		\item \color{ForestGreen} No notes to digitize right now
			\begin{itemize}
				\item Calculate maximum $e$ from Expression~\ref{eq:g6} using parameterization from paper
					\begin{itemize}
						\item Do it under simple $g$ and the more complicated $g$ from Expression~\ref{eq:g4}
						\item Compare to calculations in example from text
						\item Try another parameterization with $p$ larger so it works
					\end{itemize}
				\item Check parameter restrictions for existence of equilibria in Section 4.2
			\end{itemize}
	\end{itemize}

@@

\end{itemize}
IC constraint:
\[
  X_{FF}^l \geq p X_{FT}^l + (1-p) X_{FF}^l - g
\]
Expanded in basic terms (without efficiency issues)
\[
  \frac{W-D}{1-\de} \geq p \left[T + W + \frac{\de}{1-\de}\left(W-D\right)\right] + (1-p) \frac{W-D}{1-\de} - g
\]
Multiply through by $\left(1-\de \right)$
\[
  W-D \geq p\left(1-\de \right) \left[T + W\right] + p\de \left(W-D\right) + (1-p) \left[W-D\right] - \left(1-\de \right) g
\]
Now add complexity from Table 2
\begin{multline*}
  W(1+(1-\al_1)g_2)-D(1+(1-\al_2)g_1) \geq \\
	p\left(1-\de \right) \left[T(1+\al_2 g_1) + W(1+(1-\al_1)g_2)\right] + p\de \left(W(1+(1-\al_1)g_2)-D(1+(1-\al_2)g_1)\right) \\ + (1-p) \left[W(1+(1-\al_1)g_2)-D(1+(1-\al_2)g_1)\right] - \left(1-\de \right) g
\end{multline*}
Substitute in $\al_1 = 0$ everywhere since this is the IC for a low-type of player 1:
\begin{multline*}
  W(1+g_2) - D(1+(1-\al_2)g_1) \geq \\
	p\left(1-\de \right) \left[T(1+\al_2 g_1) + W(1+g_2) \right] + p\de \left(W(1+g_2) - D(1+(1-\al_2)g_1)\right) \\ + (1-p) \left[W(1+g_2) - D(1+(1-\al_2)g_1)\right] - \left(1-\de \right) g
\end{multline*}
Set $g_1 = 0$ on the LHS and $g_1 = g$ on the RHS:
\begin{multline*}
  W(1+g_2) - D \geq \\
	p\left(1-\de \right) \left[T(1+\al_2 g) + W(1+g_2) \right] + p\de \left(W(1+g_2) - D(1+(1-\al_2)g)\right) \\ + (1-p) \left[W(1+g_2) - D(1+(1-\al_2)g)\right] - \left(1-\de \right) g
\end{multline*}
Set $g_2 = 0$ and $\al_2 = 0$ wherever there is a $(1-p)$ and $g_2 = g$ and $\al_2 = 1$ wherever there is a $p$:
\begin{multline*}
  pW(1+g) + (1-p)W - D \geq \\
	p\left(1-\de \right) \left[T(1+g) + W(1+g) \right] + p\de \left(W(1+g) - D\right) \\ + (1-p) \left[W - D(1+g)\right] - \left(1-\de \right) g
\end{multline*}
Expand
\begin{multline*}
  pW + pWg + W - pW - D \geq \\
	\left(p-p\de \right) \left[T+Tg + W+Wg \right] + p\de \left(W+Wg - D\right) \\ + (1-p) \left[W - D -Dg\right] - \left(1-\de \right) g
\end{multline*}
Cancel some like terms and move $\left(1-\de \right) g$ to LHS
\begin{multline*}
  \left(1-\de \right) g + pWg + W - D \geq \\
	p\left[T+Tg + W+Wg \right] -p\de \left[T+Tg \right] - p\de D \\ + (1-p) \left[W - D -Dg\right] 
\end{multline*}
Do some more canceling and expanding
\begin{multline*}
  \left(1-\de \right) g + W - D \geq \\
	p\left[T+Tg + W\right] -p\de T -p\de Tg - p\de D \\ + W - D -Dg -pW +pD +pDg
\end{multline*}
\[
  \left(1-\de \right) g \geq 
	pT+pTg + pW -p\de T -p\de Tg - p\de D  -Dg -pW +pD +pDg
\]
\[
  \left(1-\de \right) g \geq pT+pTg -p\de T -p\de Tg - p\de D  -Dg +pD +pDg
\]
Now just rearrange to get all the $g$ terms on the left
\[
  \left(1-\de \right) g -pTg + p\de Tg + Dg - pDg\geq pT -p\de T - p\de D +pD
\]
\[
  \left[\left(1-\de \right) -p(1-\de)T +(1-p)D\right]g \geq p(1-\de)(T + D)
\]
\[
  g \geq \frac{p(1-\de)(T + D)}{\left(1-\de \right) -p(1-\de)T +(1-p)D}
\]
In comparing to the minimum separating gift when $e=0$, which is
\[
  g^* \geq \frac{p(1-\de)(T + D)}{\left(1-\de \right)} = p(T + D)
\]
We can simplify to see that the minimum gift when $e=1$ is larger when
\[
  (1-\de)pT > (1-p)D
\]
